\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

% Hyperlink setup - blue color, no border
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% Section formatting - professional style
\titleformat{\section}
    {\normalfont\bfseries\scshape\large}
    {}
    {0em}
    {}
\titlespacing{\section}{0pt}{10pt}{2pt}

% Add rule after section title
\newcommand{\sectionrule}{\vspace{-0.5em}\rule{\textwidth}{0.4pt}\\[0.2em]}

% Remove page numbers
\pagestyle{empty}

% Custom spacing - very tight
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\baselineskip}{1.0\baselineskip}
\setlength{\topskip}{0pt}
\sloppy

% Very tight itemize
\setlist[itemize]{
    leftmargin=15pt,
    nosep,
    topsep=0pt,
    parsep=0pt,
    itemsep=0pt,
    label=$\bullet$
}

% Custom commands for consistent formatting
\newcommand{\cvheader}[1]{{\normalsize\bfseries #1}}
\newcommand{\cvposition}[1]{{\itshape #1}}
\newcommand{\cvlocation}[1]{{\itshape #1}}
\newcommand{\cvdate}[1]{\hfill #1}

\begin{document}

% Header - Professional and clean

\begin{center}
    {\Large\bfseries MIN KI HONG}\\[4pt]
    \small
    52, Sadang-ro 17-gil, Dongjak-gu, Seoul, Republic of Korea\\
    \href{mailto:bk123477@gmail.com}{bk123477@gmail.com} \quad $\cdot$ \quad
    \href{https://bk123477.github.io/}{bk123477.github.io} \quad $\cdot$ \quad
    \href{https://github.com/bk123477}{GitHub} \quad $\cdot$ \quad
    \href{https://www.linkedin.com/in/bk123477}{LinkedIn}
\end{center}

\section{Research Interests}
\sectionrule
Generative AI; Social Norms \& Cultural Bias Mitigation; Fairness \& Inclusivity in AI; Vision-Language Models; Reasoning in LLMs \& VLMs; World Model

\section{Education}
\sectionrule
\cvheader{Carnegie Mellon University (CMU)} \cvdate{Aug 2025 -- Feb 2026}\\
\cvlocation{Pittsburgh, PA, USA},
Visiting Scholar (Short-term Research Program for six months)\\
Advisor: \textbf{Prof. Jean Oh}, Robotics Institute\\[2pt]

\cvheader{Dongguk University} \cvdate{Mar 2024 -- Feb 2026}\\
\cvlocation{Seoul, South Korea},
M.S. in Computer Science and Artificial Intelligence\\
CGPA: 4.5/4.5 $\cdot$ Advisor: \textbf{Prof. Jihie Kim}\\[2pt]

\cvheader{Dongguk University} \cvdate{Mar 2018 -- Feb 2024}\\
\cvlocation{Seoul, South Korea},
B.S. in Computer Science \& Engineering\\
CGPA: 4.07/4.5

\section{Research Experience}
\sectionrule
\cvheader{Bot Intelligence Group (BIG) at Carnegie Mellon University} \cvdate{Aug 2025 -- Feb 2026}\\
\cvposition{Visiting Scholar} $\cdot$ Supervisor: \textbf{Prof. Jean Oh}
\begin{itemize}
    \item Contributed to cultural bias evaluation in generative image models; designed cultural evaluation metrics.
\end{itemize}

\vspace{1pt}
\cvheader{Dongguk University} \cvdate{Mar 2024 -- Feb 2026}\\
\cvposition{Graduate Researcher} $\cdot$ Supervisor: \textbf{Prof. Jihie Kim}
\begin{itemize}
    \item Developed NormGenesis framework for multicultural dialogue generation via social norm modeling and violation recovery.
    \item Researched prompt engineering evaluation metrics for interpretable joint evaluation of prompts and responses.
    \item Explored visual reasoning enhancement through human-like interpretation grounding and decomposition of thought.
\end{itemize}

\section{Publications}
\sectionrule
(C: Conference, J: Journal, *: Equal contribution)\\[4pt]
[C6] Eunsoo Lee, Jeongwoo Lee, \textbf{Minki Hong}, Jangho Choi, Jihie Kim, ``VisDoT: Enhancing Visual Reasoning through Human-Like Interpretation Grounding and Decomposition of Thought,'' \textit{Findings of the 19th Conference of the European Chapter of the Association for Computational Linguistics (EACL findings).}\\[2pt]
[C5] Huichan Seo*, Sieun Choi*, \textbf{Minki Hong}*, Yi Zhou, Junseo Kim, Lukman Ismaila, Naome Etori, Mehul Agarwal, Zhixuan Liu, Jihie Kim, Jean Oh, ``Exposing Blindspots: Cultural Bias Evaluation in Generative Image Models,'' \textit{International Association for Safe and Ethical Artificial Intelligence (IASEAI'26).}~\url{https://arxiv.org/abs/2510.20042}\\[2pt]
[C4] \textbf{Minki Hong}, Jangho Choi, Jihie Kim, ``NormGenesis: Multicultural Dialogue Generation via Exemplar-Guided Social Norm Modeling and Violation Recovery,'' \textit{Proceedings of the 2025 Conference on Empirical Methods in Natural Language Processing (EMNLP 2025).} \textbf{(SAC Highlights Award)}~\url{https://arxiv.org/abs/2409.08171}\\[2pt]
[C3] \textbf{Minki Hong}, Youngsik Yun, Sohyeon Park, Jihie Kim, ``Generating Korean Image Captions using OCR in CoT Prompting,'' \textit{Annual Conference on Human and Language Technology (HCLT-KACL 2024).}\\[2pt]
[C2] Jeongwoo Lee, \textbf{Minki Hong}, Eunsoo Lee, Jihie Kim, ``LLM-based Table Data Inference using Data Augmentation and Few-Shot Prompting,'' \textit{Annual Conference on Human and Language Technology (HCLT-KACL 2024).}\\[2pt]
[C1] \textbf{Minki Hong}, Seunghyun Lee, Youn-Soon Shin, ``Proposal of an Improved Fall Detection Using GRU,'' \textit{Annual Conference of KIPS (ACK 2023).}\\[2pt]
[J1] Zainab Ullah, \textbf{Minki Hong}, Tassawar Mahmood, Jihie Kim, ``Systematic Integration of Attention Modules into CNNs for Accurate and Generalizable Medical Image Classification,'' \textit{Mathematics.}~\url{https://arxiv.org/abs/2509.05343}\\[4pt]
\vspace{2pt}
{\large\textbf{Under Review}}\\[2pt]
\textbf{Minki Hong}, Eunsoo Lee, Sohyun Park, Jihie Kim, ``Prompt Engineering Evaluation Metrics for Interpretable Joint Evaluation of Prompts and Responses.''\\[2pt]
Jahid Ullah, \textbf{Minki Hong}, Tassawar Mahmood, Jihie Kim, ``Navigating the Evolving Landscape of Continual Learning: A Review of Paradigms, Methodologies, and Open Challenges.''

\section{Intellectual Property}
\sectionrule
{\large\textbf{Patents}}\\[2pt]
\textbf{Method for Image Captioning Using OCR Information and Chain-of-Thought Prompting.} Korean Patent Application 10-2025-0138932 \cvdate{Sep 2025}\\[2pt]
\textbf{Method and System for Evaluating Prompt Engineering.} Korean Patent Application 10-2025-0106691 \cvdate{Aug 2025}\\[2pt]
\textbf{Method and System for Generating Multicultural Dialogues Based on Exemplar-Guided Social Norm Modeling.} Korean Patent Application 10-2025-0106692 \cvdate{Aug 2025}\\[4pt]
\vspace{2pt}
{\large\textbf{Software Registrations}}\\[2pt]
\textbf{Prompt Engineering Evaluation Program.} Korean Software Registration C-2025-030385 \cvdate{Aug 2025}\\[2pt]
\textbf{Exemplar-based Iterative Refinement Framework for Multicultural Social Norm Dialogue Generation.} Korean Software Registration C-2025-031729 \cvdate{Aug 2025}\\[2pt]
\textbf{Korean Captioning using CoT Prompting.} Korean Software Registration C-2025-031728 \cvdate{Aug 2025}\\[2pt]
\textbf{Korean Captioning for OCR-based Information Extraction.} Korean Software Registration C-2025-030385 \cvdate{Aug 2025}

\section{Awards}
\sectionrule
\begin{tabularx}{\textwidth}{@{}p{0.82\textwidth}>{\raggedleft\arraybackslash}X@{}}
Senior Area Chair (SAC) Highlights Award, EMNLP 2025 (\href{https://2025.emnlp.org/program/awards/}{Link}) & Nov 2025\\
Honors Graduation, Dongguk University & Feb 2024\\
Dean's List (Spring Semester), Dongguk University & Jan 2024\\
DU-Startup Challenge, Grand Prize, Dongguk University & Dec 2023\\
Dean's List (Spring Semester), Dongguk University & Jan 2023\\
\end{tabularx}


\section{Teaching Experience}
\sectionrule
\cvheader{Dongguk University} \cvdate{2023 -- 2025}\\
\cvposition{Teaching Assistant}
\begin{itemize}
    \item Software Engineering and Physical Computing (Summer 2024, 2025)
    \item Introduction to Internet of Things (Spring 2025)
    \item Adventure Design (Spring 2023, Fall 2023, Spring 2025)
    \item Capstone Design 1 \& 2 (Spring 2024, Fall 2024)
    \item Convergence Capstone Design (Fall 2024)
    \item Independent Capstone Design (Spring 2023, Fall 2023, Spring 2024)
    \item Data Structure (Spring 2024)
\end{itemize}

\vspace{1pt}
\cvheader{Korea Army Training Center} \cvdate{2020}\\
\cvposition{Assistant Instructor}
\begin{itemize}
    \item Served as assistant instructor during military service.
\end{itemize}

\section{Extracurricular Activities}
\sectionrule
\cvheader{Empirical Methods in Natural Language Processing (EMNLP 2025)} \cvdate{Nov 2025}\\
\cvposition{Volunteer Coordinator}
\begin{itemize}
    \item Served as Volunteer Coordinator, managing 160+ volunteers and overseeing main conference operations.
    \item Acted as liaison between ACL staff, volunteers, and conference participants.
\end{itemize}

\vspace{1pt}
\cvheader{Google Developer Group on Campus (GDGoC), Dongguk University} \cvdate{Aug 2024 -- Jul 2025}\\
\cvposition{AI/ML Core Member}
\begin{itemize}
    \item Led the AI/ML track as a core member.
    \item Participated in the APAC Solution Challenge 2025, developing Greenap (\href{https://github.com/bk123477/2025-APAC-SolutionChallenge-Greenap}{GitHub}).
\end{itemize}

\vspace{1pt}
\cvheader{International Joint Conference on Artificial Intelligence (IJCAI 2024)} \cvdate{Aug 2024}\\
\cvposition{Student Volunteer}
\begin{itemize}
    \item Served as a volunteer for IJCAI 2024, supporting workshop setup and operations (DemocrAI 2024, GAAMAL 2024).
\end{itemize}

\vspace{1pt}
\cvheader{Google Developer Student Club (GDSC), Dongguk University} \cvdate{Sep 2023 -- Aug 2024}\\
\cvposition{AI/ML General Member}
\begin{itemize}
    \item Actively contributed as a member in the AI/ML track, participating in seminars.
    \item Participated in the Google Solution Challenge 2024, contributing to the sMiLe project (\href{https://github.com/bk123477/2024-SolutionChallenge-sMiLe}{GitHub}).
\end{itemize}



\end{document}
